Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-28 paper/main.tex
Use a more readable font
Address all comments in the intro

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\todo[inline]{dunno if it is smart to cite Aminoff (2013) here because she also
reviews PPA + episodic memory function \& tries to unify domains via contextual
information hypothesis which is not mentioned here at all}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with different semantic
categories occurring in spoken language.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.
% Aziz' tasks:
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
jaw'').
% Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

\todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
preceding paragraph; COH: imo last two paragraphs are about exactly that??}
% summary if literature review
In summary, studies suggest that the PPA does not exclusively respond to
visually presented spatial information.
% three things in common
Nevertheless, the reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an explicit
perceptual task, experience our rich, multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Third, the reviewed studies averaged results across 7-11 participants.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures is also present under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets with
BOLD fMRI data from naturalistic and conventional block-design stimulation of
the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
% pictures -> movie -> audio-description
The movie, as an intermediate step, offered a more naturalistic but still visual
stimulation whereas the audio-description, as a further step, offered a more
naturalistic but non-visual, semantic stimulation.
% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a conventional visual localizer
for each individual, because all three operationalization capitalize on events
that should evoke the cognitive processing of spatial information.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

\todo[inline]{I searched for other studies that localize PPA: essentially every
study that does something "PPA-related" does separate localizer (using pictures
of course); but: there are two studies that evaluate localization using pictures
as such; both gave "pretty" results:}

\todo[inline]{Peelen \& Downing (2005): 6 subjects, 6x bilateral clusters
(onlinelibrary.wiley.com/doi/full/10.1002/hbm.20116)}

\todo[inline]{Downing, Peelen \& Kanwisher (2006): 12 subjects, 12x bilateral
clusters (academic.oup.com/cercor/article/16/10/1453/353981)}

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
activity levels in the PPA that were correlated with different semantic
categories occurring in \textit{speech}.
% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
% Monroe has a large square jaw'', ``The television has a long antenna''
\cite{aziz2008modulation} used sentences that described famous or generic places
and faces, or objects.
% Aziz' tasks:
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
jaw'').
% Aziz' results:
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

% summary if literature review
Taken together, the literature suggest that the PPA does not exclusively respond to
visually presented spatial information.
% three things in common
However, the reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Third, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an explicit
perceptual task, experience our rich, multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually detected by contrasting blocks of pictures is also present under more
natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both \textit{visual and
auditory} spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual spatial perception is based on an annotation of
cuts and depicted locations in the audio-visual movie ``Forrest Gump''
\citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{hausler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and naturalistic
auditory stimulation. The audio-description maintains the naturalistic nature of
the movie stimulus, but limitted to the auditory domain.
% GLM contrasts
We applied model-based, mass-univariate analyses to a series of datasets with
BOLD fMRI data from naturalistic and conventional block-design stimulation of
the same set of participants, available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}
\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a conventional visual localizer
for each individual, because all three operationalization capitalize on events
that should evoke the cognitive processing of spatial information.
%hypo b: individuals
We hypothesized further that an purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.
